\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors

### 2022-06-11 Manuscript/Lanuza_et_al_2021.Rmd
edit

This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits [@diaz2016; @carmona2021], it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits [@salguero2016]. Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds but insufficient to capture their visitation rates. This highlights the need to account for other factors such as species abundances [@ref] or biological mistmatches [@ref] to better capture the intensity of species interactions at a macroecological scale.

@@

it has been investigated empirically only just with few hundreds of Angiosperm species and without a multitrait perspective. The second axis of reproductive trait variation was the pollinator dependence axis and showed the variation

main covariation pattern of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across [@sargent2007; @kettle2011] and within [@delph2004] Angiosperms species. Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.

The second axis that explained most variation was the pollinator dependence one

Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs. Trait variation on these two axes was associated with the 'fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan. The 'slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species). In contrast, plant species that employed the 'fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence. Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010]. The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig. S11).

>>>>

This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50% and 70% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits [@diaz2016; @carmona2021], it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits [@salguero2016]. Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds. However, they were insufficient to capture their visitation rates which highlights the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.

Although the negative correlation between flower number and flower size has received substantial attention [worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other important traits like ovule number, style length and plant height also covariate along this reproductive axis.

quizas citar aqui el paper de maleness...

Hablar de los otros ejes ahora

@@

 Trait variation on these two axes was associated with the 'fast-slow continuum' in plant [@salguero2016] and animal [@healy2019] life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan. The 'slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species). In contrast, plant species that employed the 'fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence. Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display [@goodwillie2010]. The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig. S11).

### 2022-06-11 Manuscript/Lanuza_et_al_2021.tex
edit

This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}). Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds but insufficient to capture their visitation rates. This highlights the need to account for other factors (e.g., species abundances or biological mistmatch) to better capture the intensity of species interactions at a macroecological scale.

@@

it has been investigated empirically only just with few hundreds of Angiosperm species and without a multitrait perspective. The second axis of reproductive trait variation was the pollinator dependence axis and showed the variation

main covariation pattern of the reproductive trait space was the negative correlation between flower number and flower size that is a widely described association across (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}) and within (\protect\hyperlink{ref-delph2004}{Delph et al., 2004}) Angiosperms species. Our study explore this association beyond a two-trait correlation and shows that other fundamental traits to plant reproduction are also negatively correlated to flower number like ovule number and style length.

The second axis that explained most variation was the pollinator dependence one

Over half of all plant trait variation was captured by the flower number - flower size and pollinator dependence trade-offs. Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan. The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species). In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence. Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}). The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig. S11).

@@

\leavevmode\vadjust pre{\hypertarget{ref-delph2004}{}}%
Delph, L. F., Gehring, J. L., Frey, F. M., Arntz, A. M., \& Levri, M. (2004). Genetic constraints on floral evolution in a sexually dimorphic plant revealed by artificial selection. \emph{Evolution}, \emph{58}(9), 1936--1946.

>>>>

This study investigates the reproductive spectrum of flowering plants and shows that plants have clear positive and negative correlations between reproductive traits that determine interactions with floral visitors at a global scale. Despite the enormous variability of plant reproductive structures, the first two and three axes were able to capture over 50\% and 70\% of reproductive trait variation, respectively. These three axes were: (1) the flower number - flower size, (2) the pollinator dependence - floral display and (3) the style length - pollinator dependence. Although the explained trait variation that we found in the first two axes is lower than previous studies that consider morphological and physiological traits (\protect\hyperlink{ref-carmona2021}{Carmona et al., 2021}; \protect\hyperlink{ref-diaz2016}{Díaz et al., 2016}), it is consistent with the largest and most recent study that has characterised plant life strategies with reproductive and plant form and size related traits (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}). Interestingly, these different plant reproductive axes were able to partly explain the number of interacting partners of floral visitor guilds. However, they were insufficient to capture their visitation rates which highlights the need to account for other factors to better capture the strength of these mutualistic interactions at a macroecological scale.

Although the negative correlation between flower number and flower size has received substantial attention {[}worley2000; \protect\hyperlink{ref-sargent2007}{Sargent et al.} (\protect\hyperlink{ref-sargent2007}{2007}); \protect\hyperlink{ref-kettle2011}{Kettle et al.} (\protect\hyperlink{ref-kettle2011}{2011}){]}, it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. Here, we provide support to this evidence with a great diversity of phylogenetic lineages (170 families and over 1000 species) and show that other important traits like ovule number, style length and plant height also covariate along this axis.

quizas citar aqui el paper de maleness\ldots{}

Hablar de los otros ejes ahora

@@

Trait variation on these two axes was associated with the `fast-slow continuum' in plant (\protect\hyperlink{ref-salguero2016}{Salguero-Gómez et al., 2016}) and animal (\protect\hyperlink{ref-healy2019}{Healy et al., 2019}) life-history strategies, as indicated by the different floral and reproductive biology traits associated with plant height, life form and lifespan. The `slow' part of this continuum (i.e., tall trees and shrubs) included plant species with many flowers, few ovules, higher pollinator dependence, frequent occurrence of self-incompatibility and more complex breeding systems (e.g., monoecious and dioecious species). In contrast, plant species that employed the `fast' strategy (i.e., short herbs), had fewer flowers, more ovules, frequent occurrence of self-compatibility and lower pollinator dependence. Further, on the first two axes of trait variation, we found additional support for the previously described positive association between higher outcrossing rate and larger floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}). The positive correlation between larger floral display and higher pollinator dependence in our dataset further confirmed this trend (Fig. S11).

@@
